Estimating duration in the presence of misclassification

### 2024-02-19 incidence-prevalence.tex
Ch 2 Overleaf comments, except ch 7 ones

\emph{Prevalence} of a disease on day $t$, is the proportion of people with the disease on that day~\autocite[90]{lashModern}.
Within this thesis, I define an individual as having SARS-CoV-2 on day $t$ if, had they been swabbed on day $t$, that swab would return a positive RT-PCR test.
I refer to these individuals as \emph{prevalent} individuals.
I assume that an individual's prevalent status cannot change over the course of a day.
Therefore, prevalence is constant over any single day $t$.
I denote the number of prevalent individuals on day $t$ as $P_t$.
Therefore, the prevalence is $P_t/\Npop$.

>>>>

\emph{Prevalence} of a disease on day $t$, is the proportion of people with the disease on that day~\autocite[90]{lashModern}.
I refer to individuals with the disease as \emph{prevalent} individuals.
Whether an individual is prevalent is often expensive or error-prone to measure, therefore, it will often be regarded as a latent quantity.
Furthermore, what is meant by ``having'' a disease can depend on context; for example, it could be the presence of symptoms, the ability to transmit, or detectable status (the difference between these was discussed in \cref{E-biology-data:sec:natural-history})
Within this thesis, I define an individual as prevalent on day $t$ if they are detectable (detectable is defined in \cref{E-biology-data:sec:detectable}).
I assume that an individual's prevalent status cannot change over the course of a day.
Therefore, prevalence is constant over any single day $t$.
I denote the number of prevalent individuals on day $t$ as $P_t$.
Therefore, the prevalence is $P_t/\Npop$.
